![][100]

Unfortunately the process that produces the animation is still quite manual:

```{r eval=FALSE}
# Sys.setenv('R_KEEP_PKG_SOURCE'='yes')

library(watcher)
library(gganimate)
library(ggplot2)

# Generate data

set.seed(1220)
x <- runif(10)
raw <- watch(insert_sort, c('i', 'j', 'x'))(x)
dat <- simplify_data(attr(raw, 'watch.data'))
code.txt <- attr(raw, 'watch.code')

# Extract x data and augment with the corresponding scalar `j` loop index

xs <- dat$x
xs <- transform(
  xs, j=dat[['.scalar']][['j']][.id],
  ix=rep_len(seq_along(x), length(val))
)
xs[['j']][is.na(xs[['j']])] <- 0

# Display settings

dpi <- 72
width <- 600
height <- width / 3 * 2
x.size <- max(xs$ix) + 1
y.max <- max(xs[['val']])

# Plot!

p <- ggplot(xs, aes(x=ix, y=val)) +
  geom_col(aes(fill=I(ifelse(ix==j, 'red', 'grey35')))) +
  geom_label(
    data=dat[['.scalar']], aes(x=i, label='i', y=-.08*y.max),
    size=8, label.padding=unit(0.5, "lines"), family='mono'
  ) +
  geom_label(
    data=dat[['.scalar']], aes(x=j, label='j', y=-.2*y.max),
    size=8, label.padding=unit(0.5, "lines"), family='mono'
  ) +
  guides(fill=FALSE) + ylab(NULL) + xlab(NULL) +
  coord_cartesian(clip = 'off', xlim=c(0.5,max(xs$ix)+.5)) +
  geom_text(
    data=expand_text(code.txt, dat),
    aes(
      label=code, x=-x.size - 4,
      y=y.raw/(length(code.txt)*2.1),
      color=I(ifelse(highlight, 'red', 'grey35')),
      fontface=I(ifelse(highlight, 'bold', 'plain'))
    ), hjust=0, vjust=0.5, size=5, family='mono'
  ) +
  theme(
    axis.text.x=element_blank(), axis.text.y=element_blank(),
    axis.ticks.x=element_blank(), axis.ticks.y=element_blank(),
    plot.margin=unit(c(.1, .1, .1, (width/1.75)/dpi), "inches"),
    panel.grid=element_blank()
  ) +
  NULL

p.anim <- p + transition_manual(.id)

anim_save(
  '~/Downloads/sort-2.gif', nframes=length(dat$.scalar$.id), p.anim,
  width=width, height=height, fps=5
)
```
```{r echo=FALSE, eval=FALSE}
# res <- animate(
#   p.anim,
#   nframes = nrow(dat[['.scalar']]), device = "png",
#   renderer = file_renderer(
#     "~/Downloads/sort-anim-2/", prefix = "gganim-img", overwrite = TRUE
#   ),
#   width=width, height=height
# )
# ffmpeg -framerate 5 -pattern_type glob -i '*.png' -pix_fmt yuv420p out.mp4 &&
#   open out.mp4
```

There is some obvious work that could be done to make this is a bit easier.  In
particular separate the code display from the data display an only merge that at
the end so we can avoid silly alignment exercises.  It seems unlikely though
that we will be able to devise a mechanism that automatically maps variables to
aesthetics in a way that effectively clarifies the algorithm semantics.
