## Usage

`watcher` works by "instrumenting" a target function.  Consider a simple
function that adds the integers up to `n`:

```{r}
seq_sum <- function(n) {
  x <- 0
  for(i in seq_len(n)) {
    x <- x + i
  }
  x
}
res0 <- seq_sum(10)
res0
```

We can make an instrumented version of it, which will behave mostly as the
original except that the variable values at each top-level evaluation step are
attached to the result as the "watch.data" attribute:

```{r}
seq_sum_w <- watcher::watch(seq_sum)
res1 <- seq_sum_w(10)
all.equal(res0, res1, check.attributes=FALSE)
watch.dat0 <- attr(res1, 'watch.data')
str(watch.dat0[1:2])
```

Each step of the function evaluation is recorded as a list element.  This is a
bit awkward to deal with so we can use `simplify_data` to make the data more
accessible.  For example, scalar variables are turned into vectors and returned
as members of the ".scalar" data frame in the simplified list.

```{r}
watch.dat1 <- watcher::simplify_data(watch.dat0)[['.scalar']]
head(watch.dat1, 2)
```

One possible visualization is to plot variable values vs. evaluation step
(`.id`):

```{r state-vs-id, warning=FALSE}
watch.melt <- reshape2::melt(watch.dat1[c('.id', 'x', 'i')], id.vars='.id')
suppressPackageStartupMessages(library(ggplot2))
ggplot(watch.melt, aes(x=.id, y=value, color=variable)) +
  geom_point()
```


