## Usage

`watcher` works by "instrumenting" a target function.  Consider a simple
function that adds the integers up to `n`:

```{r}
seq_sum <- function(n) {
  x <- 0
  for(i in seq_len(n)) {
    x <- x + i
  }
  x
}
res0 <- seq_sum(10)
res0
```

We can make an instrumented version of it, which will behave mostly as the
original except the states of the function environment at each top-level
evaluation step are added to the result as the "watch.data" attribute:

```{r}
seq_sum_w <- watcher::watch(seq_sum)
res1 <- seq_sum_w(10)
all.equal(res0, res1, check.attributes=FALSE)
watch.dat0 <- attr(res1, 'watch.data')
str(watch.dat0[1:2])
```

Each step of the function evaluation is recorded as a list element.  This is a
bit awkward to deal with so we can use `simplify_data` to make the data more
accessible.  For example, scalar variables are turned into vectors and returned
as members of the ".scalar" data frame in the simplified list.

One possible visualization is to plot variable values vs. evaluation step
(`.id`):

```{r state-vs-id, warning=FALSE}
suppressPackageStartupMessages(library(ggplot2))
watch.dat1 <- watcher::simplify_data(watch.dat0)[['.scalar']]
watch.melt <- reshape2::melt(watch.dat1[c('.id', 'x', 'i')], id.vars='.id')

ggplot(watch.melt, aes(x=.id, y=value, color=variable)) +
  geom_point()
```


